### 2020-10-13 manuscript/manuscript.rmd
add cross_validation codes to the manuscript

```{r preliminaries}
  library( tidyverse )
  library( magrittr )
  library( viridis )
  library( knitr )
  library( gridExtra )
  library( ggpubr )
  library( grid )
  library( gtable )
  library( ggtree )
  library( ape )

@@

>>>>

```{r preliminaries}
  library( rstatix )
  library( tidyverse )
  library( magrittr )
  library( viridis )
  library( knitr )
  library( gridExtra )
  library( ggpubr )
  library( grid )
  library( gtable )
  library( ggtree )
  library( ape )

@@

![](figures/Extended_Data_Fig9.png)
**Extended Data Fig. 10.**
cross_validation =
  read_tsv("../data_processed/tables/cross_validation.tsv") %>%
  gather("model", "score", `nCAT60`, `Poisson-CAT`)

```{r cross_validation, fig.width=6, fig.height=7}
p_w = cross_validation %>%
  filter(matrix=="Whelan2017_strict") %>%
  ggplot(aes(x=model, y=score)) +
  geom_boxplot() +
  ggtitle("Whelan2017") +
  theme_classic()
p_p = cross_validation %>%
  filter(matrix=="Philippe2009_Chanimalia") %>%
  ggplot(aes(x=model, y=score)) +
  geom_boxplot() +
  ggtitle("Philippe2009") +
  theme_classic()
ggarrange(
  p_w,
  p_p,
  ncol=2, labels = c("A", "B"))

```
```{r}
# https://www.datanovia.com/en/lessons/t-test-in-r/
cross_validation %>%
  group_by(matrix,model) %>%
  get_summary_stats(score, type = "mean_sd")
# Whelan
Dw = cross_validation %>%
  filter(matrix=="Whelan2017_strict")

stat_test_w =
  t.test(score ~ model, var.equal = TRUE, data=Dw)
stat.test_w$p.value

# Philippe
Dp = cross_validation %>%
  filter(matrix=="Philippe2009_Chanimalia")

stat.test_p =
    t.test(score ~ model, var.equal = TRUE, data=Dp)
stat.test_p
stat.test_p$p.value
```
